---
title: "Homework 5"
author: "Emma Warshaw"
date: "2022-11-10"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(httr)
library(purrr)
```

## Problem 2

The Washington Post has gathered data on homicides in 50 large U.S. cities and made the data available through a GitHub repository here. You can read their accompanying article here.

Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

*The resulting data frame `homicide_data` has 12 columns and just over 52,000 rows.  The variables include uid, reported date, victim's first and last name, age, sex, city, state, latitude and longitude of the murder, and the disposition of the case.*

*I'm first grouping by `city_state` to get a summary of total homicides per city. Then, I'll isolate for cases that are marked as "Closed without arrest" or "Open/No arrest" in a second structure.  I'm also going to save these tables as tibbles for use in the second part of this question.*

```{r}
homicide_data = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")

my_homicide_df = homicide_data %>%
    mutate(
    city_state = str_c(city, state, sep = ",")
  ) 

total_homicide = my_homicide_df %>%
  group_by(city_state) %>% 
  summarise(all_homicide = n())

knitr::kable(total_homicide)

unsolved_homicide = my_homicide_df %>%
  group_by(city_state) %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  summarise(unsolved = n())

knitr::kable(unsolved_homicide)

tibble(total_homicide)
tibble(unsolved_homicide)
```

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

*From the last two summaries, we see that there were 2827 total homicides in Baltimore and 1825 of those went unsolved.  We can run a `prop.test` with this information.* 

```{r}
baltimore_prop = prop.test(1825, 2827, p = NULL, conf.level = 0.95, correct = TRUE) %>% 
  broom::tidy() %>%
  select(estimate, conf.low, conf.high)

save(baltimore_prop, file = "baltimore_prop")
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

*I'm going to combine the two tibbles I created earlier into one data frame.  Then, I'll use mapping to apply the `prop.test` to each city in the data set.* 

```{r}
homicide_props = merge(unsolved_homicide, total_homicide, by = "city_state")

each_city = homicide_props %>%
  mutate(
    props = map2(homicide_props$unsolved, homicide_props$all_homicide, prop.test),
    props = map(props, broom::tidy),
    props = map(props, ~select(.x, estimate, starts_with("conf")))
  ) %>%
  unnest(cols = c(props))
```
  
Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
each_city %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate, color = city_state)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.4) +
  theme(legend.position = "none", axis.text.x = element_text(angle = 90)) +
  labs(
    title = "Estimate and CI of Proportion of Unsolved Homicide in Each City",
    x = "city, state",
    y = "proportion + CI"
  )
```

## Problem 3

When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a one-sample t-test.

First set the following design elements:

Fix n=30
Fix σ=5
Set μ=0. Generate 5000 datasets from the model

x∼Normal[μ,σ]

For each dataset, save μ̂ and the p-value arising from a test of H:μ=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

```{r}
sim_function = function(n = 30, mu, sigma = 5) {
  sim_data = 
    tibble(
      x = list(rnorm(n, mu, sigma)))
    return(sim_data)
}

output = tibble()

for (i in 1:5000) {
  output[[i]] = bind_rows(output, sim_function(mu = 0))
}

mu0 = output 

t_test_mu0 = mu0 %>%
  t_test_res = map(.x = x, ~t.test(.x) %>% broom::tidy)

```

Repeat the above for μ={1,2,3,4,5,6}, and complete the following:
```{r}
##Mu = 1
for (i in 1:5000) {
  output[[i]] = bind_rows(output, sim_function(mu = 1))
}

mu1 = output

## mu = 2
for (i in 1:5000) {
  output[[i]] = bind_rows(output, sim_function(mu = 2))
}

mu2 = output

## mu = 3
for (i in 1:5000) {
  output[[i]] = bind_rows(output, sim_function(mu = 3))
}

mu3 = output

## mu = 4
for (i in 1:5000) {
  output[[i]] = bind_rows(output, sim_function(mu = 4))
}

mu4 = output

## mu = 5
for (i in 1:5000) {
  output[[i]] = bind_rows(output, sim_function(mu = 5))
}

mu5 = output

## mu = 6
for (i in 1:5000) {
  output[[i]] = bind_rows(output, sim_function(mu = 6))
}

mu6 = output

```


Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

```{r}

```

Make a plot showing the average estimate of μ̂  on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂  only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ̂  across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

```{r}

```


